Predicting Solid State Qubit Candidates

### 2021-08-18 paper.tex
Updates from Overleaf

\section*{Theoretical Background and Experimental Data} 
%Subsections are potential topics, not necessarily subsections we will actually include. 
%We can probably merge a few of the subsections in the end, or even move some theory to the supplementary

@@

@@

The work of MHJ is supported by the U.S. Department of Energy,
Office of Science, office of Nuclear Physics under grant
No. DE-SC0021152 and U.S. National Science Foundation Grants
No. PHY-1404159 and PHY-2013047. 
The work of MEB and LV was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
MEB acknowledges support by an ETH Zurich Postdoctoral Fellowship.

>>>>

\section*{Theoretical Background and Experimental Data}

@@

Density functional theory is a versatile and powerful theoretical approach, enabling targeted study of semiconductor materials with many atoms. 
Proven successful for material properties such as thermal stability, lattice parameters and band gap.

@@

The work of MHJ is supported by the U.S. Department of Energy,
Office of Science, office of Nuclear Physics under grant
No. DE-SC0021152 and U.S. National Science Foundation Grants
No. PHY-1404159 and PHY-2013047. 
The work of MEB and LV was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship.
